Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-12 paper/paper.tex
#25 add results to manuscript

>>>>

\section{Empirical strategy}

First I replicate the long-term finding of \cite{schoenholzer2022} using the following equation:

\begin{equation}
    construction_{it} = \alpha_i + \delta_t + \mathbf{1}(S_{it} > 0) + 
    \sum_{\tau = -100}^{200} \mathbf{1}(t = e^{NewState}_i + \tau)\pi_t + \varepsilon_{it}
\end{equation}

I can barely believe it myself, but I replicate their finding:

\begin{figure}
    \centering
    \includegraphics[scale = 0.4]{paper/output/regressions/SW22_replication_50y.png}
    \caption{It looks just like it's supposed to!}
    \label{fig:SW_replication}
\end{figure}

Next I tried to find the effect of state power - the effect of the difference in selection for state power between conquests and successions:

\begin{multline}
    construction_{it} = \alpha_i + \delta_t + \mathbf{1}(S_{it} > 0) +
    \mathbf{1}(t \ge e^{NewState}_i)\beta +
    \mathbf{1}(t \ge e^{NewState}_i) \times C_i \theta + \varepsilon_{it}
\end{multline}

Unfortunately it's not as convincing:

\input{paper/output/regressions/baseline_50y}
